### 2022-03-30 README.Rmd
EL2 classed replaced by EL class. function pointer is used for setting methods such as estimating function and gradient function.
README, DESCRIPTION updated

## Usage
```{r eval = TRUE}
library(melt)
# one sample test (mean) 
el_mean(par = 0, x = rnorm(n = 100))

# linear regression
fit <- el_lm(formula = mpg ~ wt, data = mtcars)
summary(fit)

# analysis of variance
el_aov(formula = Sepal.Length ~ Species, data = iris)
```

>>>>

## Usage
```{r eval = TRUE}
library(melt)
# one sample test for mean
fit1 <- el_mean(par = 0, x = rnorm(n = 100))
confint(fit1)

# linear regression
fit2 <- el_lm(formula = mpg ~ wt, data = mtcars)
summary(fit2)
confint(fit2)

# analysis of variance 
data("clothianidin")
fit3 <- el_lm(clo ~ -1 + trt, clothianidin)
summary(fit3)
confint(fit3)

# test of no treatment effect
lhs <- matrix(c(1, -1, 0, 0,
                0, 1, -1, 0,
                0, 0, 1, -1), byrow = TRUE, nrow = 3)
lht(fit3, lhs)
```
